Hierarchy Builder

### 2020-04-27 coqws/easychair.tex
final
fixes

The details of \HB{}, including its compilation to the (Flat) Packed Classes
discipline and its implementation in the Elpi extension language for Coq,
are given in~\cite{cohen:hal-02478907}.
In this talk we focus on how to use \HB{} in a Coq development,
% and we plan to not detail how it works behind the scenes, 
unless questions on its internals arise from the audience.\\
\HB{} is available for download at \url{https://github.com/math-comp/hierarchy-builder}

@@

HB.mixin Record SemiRing_of_CMonoid A of CMonoid A := {
  one    : A;
  mul    : A -> A -> A;
  mulrA  : associative mul;  (* `mul` is associative   *)
  mul1r  : left_id one mul;  (* `one` is left neutral  *)
  mulr1  : right_id one mul; (* `one` is right neutral *)
  mulrDl : left_distributive mul add;  (* `mul` distributes over *)
  mulrDr : right_distributive mul add; (*   `add` on both sides  *)
  mul0r  : left_zero zero mul;  (* `zero` is absorbing `mul`     *)
  mulr0  : right_zero zero mul; (*   on both sides               *)
}.
HB.structure Definition SemiRing := { A of SemiRing_of_CMonoid A & }.
Notation "1"  := one.
Notation "-1" := (- one).
Infix    "*"  := mul.

(* A statement in the signature of a `SemiRing` S.  *)
Check forall S : SemiRing.type, forall x : S, x * 1 + 0 = x.

(* We need no additional mixin to declare the `Ring` structure. *)
HB.structure Definition Ring := { A of SemiRing_of_CMonoid A & AbelianGrp_of_CMonoid A }.

(* A statement in the signature of a Ring R.  *)
Check forall R : Ring.type, forall x : R, x * -1 = - x.

(* We equip Z with the structures of CMonoid, AbelianGrp and SemiRing; HB equips it with Ring. *)
Definition Z_CMonoid    := CMonoid_of_Type.Build Z 0%Z Z.add Z.add_assoc Z.add_comm Z.add_0_l.
HB.instance Z Z_CMonoid.
Definition Z_AbelianGrp := AbelianGrp_of_CMonoid.Build Z Z.opp Z.add_opp_diag_l.
HB.instance Z Z_AbelianGrp.
Definition Z_SemiRing   := SemiRing_of_CMonoid.Build Z 1%Z Z.mul Z.mul_assoc Z.mul_1_l
  Z.mul_1_r Z.mul_add_distr_r Z.mul_add_distr_l (fun _ => erefl) Zmult_0_r.
HB.instance Z Z_SemiRing.

>>>>

The details of \HB{}, including its compilation to the (Flat) Packed Classes
discipline and its implementation in the Elpi extension language for Coq,
are given in~\cite{cohen:hal-02478907}.
In this talk we focus on how to use \HB{} in a Coq development,
% and we plan to not detail how it works behind the scenes, 
unless questions on its internals arise from the audience.\\
\HB{} is available for download at \url{https://github.com/math-comp/hierarchy-builder}.

@@

HB.mixin Record SemiRing_of_CMonoid A of CMonoid A := {
  one    : A;
  mul    : A -> A -> A;
  mulrA  : associative mul;  (* `mul` is associative   *)
  mul1r  : left_id one mul;  (* `one` is left neutral  *)
  mulr1  : right_id one mul; (* `one` is right neutral *)
  mulrDl : left_distributive mul add;  (* `mul` distributes over *)
  mulrDr : right_distributive mul add; (*   `add` on both sides  *)
  mul0r  : left_zero zero mul;  (* `zero` is absorbing `mul`     *)
  mulr0  : right_zero zero mul; (*   on both sides               *)
}.
HB.structure Definition SemiRing := { A of SemiRing_of_CMonoid A & }.
Notation "1"  := one.
Infix    "*"  := mul.

(* A statement in the signature of a Semiring S.  *)
Check forall S : SemiRing.type, forall x : S, x * 1 + 0 = x.

(* We need no additional mixin to declare the Ring structure. *)
HB.structure Definition Ring := { A of SemiRing_of_CMonoid A & AbelianGrp_of_CMonoid A }.

(* A statement in the signature of a Ring R.  *)
Check forall R : Ring.type, forall x : R, x * - (1) = - x.

(* We equip Z with CMonoid, AbelianGrp and SemiRing structures; HB equips it with Ring. *)
Definition Z_CMonoid    := CMonoid_of_Type.Build Z 0%Z Z.add Z.add_assoc Z.add_comm Z.add_0_l.
HB.instance Z Z_CMonoid.
Definition Z_AbelianGrp := AbelianGrp_of_CMonoid.Build Z Z.opp Z.add_opp_diag_l.
HB.instance Z Z_AbelianGrp.
Definition Z_SemiRing   := SemiRing_of_CMonoid.Build Z 1%Z Z.mul Z.mul_assoc Z.mul_1_l ...
HB.instance Z Z_SemiRing.
